Mixture Modeling Paper Results

### 2017-03-19 PaperEx170308.Rmd
Changed from 90&95 to 80&90

standindetobject1<-standindet(uncertobj=uncertobject1,multcutobj=multcutobject1,cutcomp=1)
specindetobject1<-specindet(uncertobj=uncertobject1,multcutobj=multcutobject1,cutcomp=1,certlevel=0.8)

>>>>

standindetobject1<-standindet(uncertobj=uncertobject1,multcutobj=multcutobject1,cutcomp=1)
specindetobject1<-specindet(uncertobj=uncertobject1,multcutobj=multcutobject1,cutcomp=1,certlevel=0.95)
